---
title: "BA Assignment-3"
author: "Abhinay Chiranjeeth Marneni"
date: "2022-11-13"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# 1)To create the variables X and Y, run the following code.
```{r}
set.seed(2017) 
X=runif(100)*10 
Y=X*4+3.45 
Y=rnorm(100)*0.29*Y+Y 
```

## a) Creating Plot for X and Y variables, the plot will allow us to fit a linear model to explain Y based on X.
```{r}
plot(X,Y)  
# Yes, We are able to fit a linear model to Y given X.
```

## b) Create a simple linear model of Y based on X.And find the accuracy of linear model.

```{r}
Model<-lm(Y~X)
Model$coefficients
Accuracy<- 3.610759/4.465490
Accuracy  # The accuracy of above linear model is 0.8085919
```

## c) The correlation between X and Y is related to the Coefficient of Determination, R2, of the above linear model.
```{r}
(cor(Y,X))^2  # To find Coefficient of Determination of model we using the                        code (Correlation Coefficient)^2
```

# 2) Utilize the mtcars dataset.
```{r}
data<-data("mtcars")
head(mtcars)
```
## a) James wants to buy a car.  He and his friend, Chris, have different opinions about the Horse Power (hp) of cars. James think the weight of a car (wt) can be used to estimate the Horse Power of the car while Chris thinks the fuel consumption expressed in Mile Per Gallon (mpg), is a better estimator of the (hp). Who do you think is right? Construct simple linear models using mtcars data to answer the question. 
```{r}
Weight <- lm(mtcars$wt ~ mtcars$hp) # James opinion
Mile <- lm(mtcars$mpg ~ mtcars$hp)  # Chris opinion
summary(Weight)
summary(Mile)
# By looking at the multiple r-squared values, Chris is right; Mile Per Gallon had a high r square value of 60 percent compared to weight of the car's 43 percent.
```
## b) Build a model that uses the number of cylinders (cyl) and the mile per gallon (mpg) values of a car to predict the car Horse Power (hp). Using this model, what is the estimated Horse Power of a car with 4 calendar and mpg of 22.
```{r}
Model1<-lm(hp ~cyl + mpg, data = mtcars)
Model1
```
# To perdict the car horse power.
```{r}
HP <- 54.067 + (23.979 *4) + (-2.775 * 22)
HP
```
# 3) Install "mlbench" packages and Loading the "BostonHousing" dataset.
```{r}
library(mlbench)
data(BostonHousing)
```

## a)Build a model to estimate the median value of owner-occupied homes (medv)based on the following  variables:  crime  crate  (crim),  proportion  of  residential  land  zoned  for  lots  over  25,000  sq.ft  (zn),  the  local  pupil-teacher  ratio  (ptratio)  and  weather  the  whether  the  tract  bounds Chas River(chas). Is this an accurate model.

```{r}
Accuracy1<- lm(medv~crim+zn+ptratio+chas,data=BostonHousing)
summary(Accuracy1)
# Due to the low R square value, the model is not accurate.
```
## b)
##i) Imagine two houses that are identical in all aspects but one bounds the Chas River and the other does not. Which one is more expensive and by how much.
```{r}
CR1 <- lm(medv ~ chas == 1, data = BostonHousing) # Price not next to river
summary(CR1)
CR2 <- lm(medv ~ chas == 0, data = BostonHousing) # Price next to river 
summary(CR2)
# The cost of a house with a chas of 1 is higher than a house without a chas of 0
```

## ii) Imagine two houses that are identical in all aspects but in the neighborhood of one of them the pupil-teacher ratio is 15 and in the other one is 18. Which one is more expensive and by how much.
```{r}
summary(HP2<-lm(medv~ptratio,data = BostonHousing))
 # If ptratio increases the housing price decreases,The price of house which has ptratio of 15 is high compared to price of house which has a ptratio of 18.
```

# c) Which of the variables are statistically important.
```{r}
summary(Accuracy1)
#  So the all varaiables in the model are Statistically important.
```

# d) Use the anova analysis and determine the order of importance of these four variables. 

```{r}
anova(Accuracy1)
## order of Importance of the varaiables 
## 1) crim
## 2) zn
## 3) ptratio
## 4)chas
```